ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura G\'ati).}

### 2018-07-03 Latex/Draft_Summer2018/Summer2018.tex
keep writing, reviewing some technicalities

Using a notation similar to \cite{barsky2011news}, we implement our identification strategy as follows. Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$ presented above. One can form the reduced form moving average representation:
$$
y_t = \bar{B}(L)y_{t} + i_t \ \ \Rightarrow \ \ y_t = A(L)i_t
$$
where $A(L) = [I - \bar{B}(L)]^{-1}$ and $\bar{B}(L)$ has no constant terms. Assume now that there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$:
$$
s_t = A_0 i_t
$$
This entails the structural moving average representation:
$$
y_t = C(L)i_t
$$
where $C(L) = A(L) A_0$ and $i_t = A_0^{-1} s_t$. The impact matrix $A_0$ must be such that $\Sigma = A_0 A_0'$. Notice that $A_0$ is not unique since for any $D$ such that $DD' = I$, $\tilde{A}_0 = A_0 D$ satisfies $\Sigma = \tilde{A}_0 \tilde{A}_0'$.

@@

Using the same notation in Section \ref{section:empiricalstrategy_simple}, our identification strategy can be presented as follows,\footnote{Also in this case we keep following the same notation of \cite{barsky2011news}.}

@@

\textbf{Step 1 - Identification of $\gamma_{news}$}
$$
\max_{\gamma_{news}} \sum_{h = 0}^{H} \Sigma
$$

>>>>

Using a notation similar to \cite{barsky2011news}, we implement our identification strategy as follows. Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$ presented above. The reduced-form VAR takes the following form,
$$
y_t = B(L)y_{t-1} + i_t 
$$
Assume now that there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$,
$$
A_0 s_t = i_t
$$
which implies the structural-form VAR
$$
A_0^{-1}y_t = C(L) y_{t-1} + s_t
$$
where $C(L) = A_0^{-1} B(L)$ and $s_t = A_0^{-1} i_t$. The impact matrix $A_0$ must be such that $\Sigma = A_0 A_0'$. Notice that $A_0$ is not unique since for any $D$ such that $DD' = I$, $\tilde{A}_0 = A_0 D$ satisfies $\Sigma = \tilde{A}_0 \tilde{A}_0'$.

@@

Using a similar notation in Section \ref{section:empiricalstrategy_simple}, assume for simplicity  that $B(L)$ allows only of one lag

@@

\textbf{Step 1 - Identification of $\gamma_{news}$}
$$
\max_{\gamma_{news}} \frac{\sum_{\tau = 0}^H B_{}}{}
$$
